\bf\mftitle

### 2011-03-02 doc/jInfer/tutorials/doc_tutorial_dev.tex
Documentation: Tutorials: changing titles.
minor to building, tutorial_dev is OK

\def\mftitle{Module Developer's Tutorial}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\begin{enumerate}
  \item Expand the jInfer suite (brown puzzles icon).
  \item Right-click \textit{Modules}, select \textit{Add New...}.
  \item On the first page, pick a name for your module. Click \textit{Next}.
  \item On the second page, fill out the following:
    \begin{itemize}
      \item 
        \textit{Code base}: this will be the package structure in which your code is placed.
        If you want, follow our convention: \texttt{cz.cuni.mff.ksi.jinfer.\textit{yourmodule}}.
        Otherwise choose something like \texttt{\textit{tld.company.jinfer.yourmodule}}.

@@

  \item Click \textit{Finish}.
\end{enumerate}
\subsection*{Implement jInfer's specifics}
\par 
This section will show how to deal with a new inference module - a simplifier
that does no actual simplification, just returns the grammar it got on input.
Your module will need a "main" class implementing the chosen inference
interface, annotated with a \texttt{@ServiceProvider} annotation.

\par 
But first, we need to do some setup.
\begin{enumerate}
  \item Right-click the newly created module, select \textit{Properties}.
  \item In \textit{Libraries > Module Dependencies}, click \textit{Add Dependency...}.
  \item Filter for "base" and select \textit{Base} as a dependency. Click \textit{OK}.
  \item 
      Still in \textit{Properties}, switch to \textit{Display} category. Fill in:
      \begin{itemize}
        \item \textit{Display Name}: Fill in a user-friendly name of your module.
        \item \textit{Display Category}: type in \textit{jInfer}.
        \item \textit{Short \& Long Description}: unleash your inner poet!
      \end{itemize}

@@

\par 
Now to the class itself.
\begin{enumerate}
  \item Add a new Java class: right click \textit{Source Packages} in your new
      module, select \textit{New > Java Class...}.
  \item Fill in class name, for example \textit{MySimplifierImpl}.
  \item Fill in package based on the \textit{Code base} you selected while creating
      the module itself.
  \item Click \textit{Finish}.
  \item In the heading line of the class, add \texttt{implements Simplifier} and
      fix the imports (you need \texttt{Simplifier} from Base module).
  \item Annotate this class with \texttt{@ServiceProvider(service = Simplifier.class)}.
  \item NetBeans will complain about missing method implementations, add them.
  \item 
    Now fill in method bodies:
    \begin{itemize}
      \item \texttt{getName()}: return a string with module unix name, for example \texttt{"mysimplifier"}.
      \item \texttt{getDisplayName()}: return a user friendly module name, for example \texttt{"My First Simplifier"}.
      \item \texttt{getModuleDescription()}: return a short module description. You can also return \texttt{getDisplayName()} in this case.
      \item \texttt{getCapabilities()}: for the moment, it is enough to return \texttt{Collections.emptyList()}.
      \item \texttt{start()}: here is where your main logic belongs. In the case of a simplifier, you would do something with the rules and return a simplified grammar. For now, just do \texttt{callback.finished(initialGrammar);}
    \end{itemize}

>>>>

\def\mftitle{jInfer Module Developer's Tutorial}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\begin{enumerate}
  \item Expand the jInfer suite (brown puzzles icon).
  \item Right-click \textit{Modules}, select \textit{Add New...}.
  \item On the first page, pick a name for your module. Click \textit{Next}.
  \item On the second page, fill out the following:
    \begin{itemize}
      \item 
        \textit{Code base}: this will be the package structure in which your code is placed.
        If you want, follow our convention: \texttt{cz.cuni.mff.ksi.jinfer.\textit{yourmodule}}.
        Otherwise choose something like \texttt{\textit{tld.\.company.\.jinfer.\.yourmodule}}.

@@

  \item Click \textit{Finish}.
\end{enumerate}
\subsection*{Implement jInfer's specifics}
\par 
This section will show how to deal with a new inference module - a simplifier
that does no actual simplification, just returns the grammar it got on input.
Your module will need a ``main'' class implementing the chosen inference
interface, annotated with a \texttt{@ServiceProvider} annotation.

\par 
\noindent But first, we need to do some setup.
\begin{enumerate}
  \item Right-click the newly created module, select \textit{Properties}.
  \item In \textit{Libraries > Module Dependencies}, click \textit{Add Dependency...}.
  \item Filter for ``base'' and select \textit{Base} as a dependency. Click \textit{OK}.
  \item 
      Still in \textit{Properties}, switch to \textit{Display} category. Fill in:
      \begin{itemize}
        \item \textit{Display Name}: Fill in a user-friendly name of your module.
        \item \textit{Display Category}: type in \textit{jInfer}.
        \item \textit{Short \& Long Description}: unleash your inner poet!
      \end{itemize}

@@

\par 
\noindent Now to the class itself.
\begin{enumerate}
  \item Add a new Java class: right click \textit{Source Packages} in your new
      module, select \textit{New > Java Class...}.
  \item Fill in class name, for example \textit{MySimplifierImpl}.
  \item Fill in package based on the \textit{Code base} you selected while creating
      the module itself.
  \item Click \textit{Finish}.
  \item In the heading line of the class, add \texttt{implements Simplifier} and
      fix the imports (you need \texttt{Simplifier} from Base module).
  \item Annotate this class with \texttt{@ServiceProvider(service = Simplifier.class)}.
  \item NetBeans will complain about missing method implementations, add them.
  \item 
    Now fill in method bodies:
    \begin{itemize}
      \item \texttt{getName()}: return a string with module unix name, for example \texttt{``mysimplifier''}.
      \item \texttt{getDisplayName()}: return a user friendly module name, for example \texttt{``My First Simplifier''}.
      \item \texttt{getModuleDescription()}: return a short module description. You can also return \texttt{getDisplayName()} in this case.
      \item \texttt{getCapabilities()}: for the moment, it is enough to return \texttt{Collections.emptyList()}.
      \item \texttt{start()}: here is where your main logic belongs. In the case of a simplifier, you would do something with the rules and return a simplified grammar. For now, just do \texttt{callback.finished(initialGrammar);}
    \end{itemize}
